Modern Graph Generators: A Survey

### 2018-09-24 data_sets.tex
Sherif Changes

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists and edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex is a product and an edge between two products
    exists if a person has bought the two products.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges the acquitances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges the hyperlinks connecting them.
\end{itemize}

@@

Many recommender systems are based on graphs, either bipartite graphs or
many-to-many graphs. Such systems are usually tested on several real-world datasets,
many of them containing information about rating of products or other items such
as movies, books or songs. The following are the most widely used datasets for
testing recommender systems:

@@

  \begin{itemize}
    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
      several Bitcoin exchanges, where users are able to rate other users after
      their transactions. Here, the vertices represent the users and the edges,
      which are labelled, the ratings between them.
    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This is a network extracted
      from Wikipedia, where the vertices represent users  and the
      edges, which are labelled, the votes emitted by administrators for the
      user to become an administrator.  Each vote is accompained with a text
      explaining the vote's sign.
    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
      editors where the vertices are the editors and the edges, which are
      labelled, represent the turst level between two editors.
    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
      the Epinions network which also contains the levels of distrust between the
      users, expressed by means of edges between them.
    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
      a Twitter network where vertices represent users and there is an edge
      between two users if a user mentions another one in a tweet. The edges
      are labelled with the average sentiment of one user towards another.
  \end{itemize}

@@

Many of the already discussed datasets are also typically used to test and
compare graph partitioning, clustering and community detection algorithms. One
can find a comprehensive list of datasets for such algorithms
in~\cite{10dimacs,yang2015defining}, some of them already discussed for other
applications. Here, we summarize the most widely used in the literature:

\begin{itemize}
  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
    are widely used for evaluating community detection since they provide
    information about the meta-communities they contain. For instance, in
    Livejournal, users can join groups of users talking about given topics. Such
    groups are exported as meta-communities, and similar approaches are used for
    other graphs. Community detection algorithms are then evaluated by trying to
    infer such meta-communities without prior knowledge of the user to group
    assignment.
  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
    of a small network of members of a karate club that was dismissed and split
    into two new karate clubs. Vertices represent persons and edges friendship
    relationships. Information about what people joined each of the two new
    karate clubs is provided.
  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
    blogs talking about the US 2005 political elections, where a vertex
    represents a blog and the edges the hyperlinks between the blogs. Each blog
    has an associated label, whether it is left or right oriented.
  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
    about politics, and edges between two books exist if they are co-purchased
    together. The books have labels of whether they are left or right oriented.
  \item \textbf{Football}~\cite{girvan2002network}: A network of american university
    football teams. Each node represents a football team and the edges represent
    the matches between them during the season. Each team is associated to a
    division.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{Higgs-Twitter}~\cite{de2013anatomy}: This dataset contains the Twitter
    network before, during and after the discovery of the Higgs boson.
    Concretely, it contains the tweets, the mentions, retweets,
    followers/followees, etc.
  \item \textbf{Memetracker}~\cite{leskovec2009meme}: Memetracker is a dataset that
    contains the quotes and phrases that appear more frequently on the entire
    news spectrum. It consists of the links of the news, the time and memes, and
    is used to understand how information spawns, evolves and dies.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{DbPedia}~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
    a structured version of Wikipedia. It allows users to semantically query the
    relationships between the different resources at Wikipedia.
  \item \textbf{Freebase}~\cite{bollacker2008freebase}: Is a collaborative knowledge base
    made of metadata mainly provided by community members. It contains
    structured data from multiple sources in an attempt to create a global
    resource of information accessible both from persons and machines. The
    project was discontinued in 2014 and replaced by Wikidata.
  \item \textbf{Yago}~\cite{suchanek2007yago}, \textbf{Yago2}~\cite{hoffart2013yago2} \&
    \textbf{Yago3}~\cite{mahdisoltani2013yago3}: These are
    open source knowledge bases developed at the Max Planck Institute of
    Computer Science in Saarbr\"ucken. They contain structured data automatically extracted
    from Wikipedia and other sources.
  \item \textbf{Wikidata}~\cite{vrandevcic2014wikidata}: This is a knowledge base
    collaboratively edited by the community and hosted by the Wikimedia
    Foundation. It contains structured data from its sister projects Wikipedia,
    Wikivoyage, Wikisource and others.
  \item \textbf{Billion Triple Challenge}~\cite{btc-2014}: This is a semantic dataset
    crawled from different sources, including Freebase, DBPedia or the BBC. A
    detailed description of the crawling process can be found in~\cite{kafer2012towards}.
\end{itemize}

>>>>

Large scale graph analytics systems are usually benchmarked using a combination of
real-world and synthetically generated graphs. Because of the rapid evolution of such
systems and their increasing capability to process larger graphs, the datasets
typically used  in the literature quickly change overtime. The most commonly
used datasets (which can be downloaded from several graph dataset
repositories~\cite{snapnets,lawalgo}) are:
\begin{itemize}
  \item \textbf{DBLP}~\cite{yang2015defining}: Represents a co-authorship network where
    researchers from DBLP are represented as vertices and there exists an edge
    between them if they have published a paper together.
  \item \textbf{Amazon}~\cite{yang2015defining}: Represents a product co-purchasing
    network, such that each vertex is a product and an edge between two products
    exists if a person has bought the two products.
  \item \textbf{Road networks}~\cite{leskovec2009community}: Consist of a set of road
    networks from the US.
  \item \textbf{LiveJournal}~\cite{yang2015defining}: A social network where vertices
    represent the users and the edges represent the acquitances between them.
  \item \textbf{Orkut}~\cite{yang2015defining}: Like LiveJournal, this is a social network
    where vertices represent persons and the edges represent their friendships.
  \item \textbf{Twitter}~\cite{kwak2010twitter}: This is a directed network representing
    the follower-followee interaction of Twitter.
  \item \textbf{Friendster}~\cite{yang2015defining}: A social network like LiveJournal and
    Orkut, where nodes represent persons and edges their relationships.
  \item \textbf{WebUK}~\cite{delis}: A web graph of the UK subdomain, where nodes represent
    websites and edges represent the hyperlinks between them.
  \item \textbf{ClueWeb2012}~\cite{clueweb}. This is a crawl of the web from 2012, where
    vertices represent websites and the edges represent the hyperlinks connecting them.
\end{itemize}

@@

Many recommender systems are based on graphs, either bipartite graphs or
many-to-many graphs. Such systems are usually tested on several real-world datasets,
many of them containing information about the rating of products or other items such
as movies, books or songs. The following are the most widely used datasets for
testing recommender systems:

@@

  \begin{itemize}
    \item \textbf{Bitcoin}~\cite{moore2013beware}: This dataset contains information from
      several Bitcoin exchanges, where users are able to rate other users after
      their transactions. Here, the vertices represent the users and the edges,
      which are labelled, the ratings between them.
    \item \textbf{Wikipedia RFA}~\cite{west2014exploiting}: This is a network extracted
      from Wikipedia, where the vertices represent users  and the
      edges, which are labelled, the votes emitted by administrators for the
      user to become an administrator.  Each vote is accompained with a text
      explaining the vote's sign.
    \item \textbf{WikiSigned}~\cite{maniu2011building}: This is a network of Wikipedia
      editors where the vertices are the editors and the edges, which are
      labelled, represent the trust level between two editors.
    \item \textbf{Extended Epinions}~\cite{massa2007trust}: This is an extended version of
      the Epinions network which also contains the levels of distrust between the
      users, expressed by means of edges between them.
    \item \textbf{Twitter Indian Elections}~\cite{kagan2015using}: This network represents
      a Twitter network where vertices represent users and there is an edge
      between two users if a user mentions another one in a tweet. The edges
      are labelled with the average sentiment of one user towards another.
  \end{itemize}

@@

Many of the already discussed datasets are also typically used to test and
compare graph partitioning, clustering and community detection algorithms. One
can find a comprehensive list of datasets for such algorithms
in~\cite{10dimacs,yang2015defining}, some of which we have already discussed for other
applications. Here, we summarize the most widely used in the literature:

\begin{itemize}
  \item \textbf{DBLP}, \textbf{Amazon}, \textbf{LiveJournal}, \textbf{Orkut} and \textbf{Friendster}~\cite{yang2015defining}
    are widely used for evaluating community detection since they provide
    information about the meta-communities they contain. For instance, in
    Livejournal, users can join groups of users talking about given topics. Such
    groups are exported as meta-communities, and similar approaches are used for
    other graphs. Community detection algorithms are then evaluated by trying to
    infer such meta-communities without prior knowledge of the user to group
    assignment.
  \item \textbf{Zachary Karate Club}~\cite{zachary1977information}: This graph consists
    of a small network of members of a karate club that was dismissed and split
    into two new karate clubs. Vertices represent persons and edges friendship
    relationships. Information about what people joined each of the two new
    karate clubs is provided.
  \item \textbf{PolBlogs}~\cite{adamic2005political}: This is a network consisting of
    blogs talking about the US 2005 political elections, where a vertex
    represents a blog and the edges the hyperlinks between the blogs. Each blog
    has an associated label, whether it is left or right oriented.
  \item \textbf{PolBooks}~\cite{10dimacs}: Is a network of books of Amazon that talk
    about politics, and edges between two books exist if they are co-purchased
    together. The books have labels of whether they are left or right oriented.
  \item \textbf{Football}~\cite{girvan2002network}: A network of American university
    football teams. Each node represents a football team and the edges represent
    the matches between them during the season. Each team is associated to a
    division.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{Higgs-Twitter}~\cite{de2013anatomy}: This dataset contains the Twitter
    network before, during and after the discovery of the Higgs boson.
    Specifically, it contains the tweets, the mentions, retweets,
    followers/followees, etc.
  \item \textbf{Memetracker}~\cite{leskovec2009meme}: Memetracker is a dataset that
    contains the quotes and phrases that appear more frequently on the entire
    news spectrum. It consists of the links of the news, the time and memes, and
    is used to understand how information spawns, evolves and dies.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{DbPedia}~\cite{Bizer:2009:DCP:1640541.1640848}: The DBPedia project aims at creating
    a structured version of Wikipedia. It allows users to semantically query the
    relationships between the different resources at Wikipedia.
  \item \textbf{Freebase}~\cite{bollacker2008freebase}: This is a collaborative knowledge base
    made of metadata that is mainly provided by community members. It contains
    structured data from multiple sources in an attempt to create a global
    resource of information accessible both from persons and machines. The
    project was discontinued in 2014 and replaced by Wikidata.
  \item \textbf{Yago}~\cite{suchanek2007yago}, \textbf{Yago2}~\cite{hoffart2013yago2} \&
    \textbf{Yago3}~\cite{mahdisoltani2013yago3}: These are
    open source knowledge bases developed at the Max Planck Institute of
    Computer Science in Saarbr\"ucken. They contain structured data  that has been automatically extracted
    from Wikipedia and other sources.
  \item \textbf{Wikidata}~\cite{vrandevcic2014wikidata}: This is a knowledge base
    collaboratively edited by the community and hosted by the Wikimedia
    Foundation. It contains structured data from its sister projects Wikipedia,
    Wikivoyage, Wikisource and others.
  \item \textbf{Billion Triple Challenge}~\cite{btc-2014}: This is a semantic dataset
    crawled from different sources, including Freebase, DBPedia or the BBC. A
    detailed description of the crawling process can be found in~\cite{kafer2012towards}.
\end{itemize}

### 2018-09-24 generators.tex
Sherif Changes

In this section we explore in more detail different graph data generators using the classification introduced before. For each category we briefly describe key features of each of the representatives. The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.

>>>>

In this section we explore in more detail the different graph data generators using the classification introduced before. For each category we briefly describe the key features of each of the representative examples. The aim is to provide the readers with a detailed look at each of the tools in the context of its competitors from the same domain.

### 2018-09-24 generators_GraphDatabases.tex
Sherif Changes

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks designed particularly for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590}. Or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark specific for graph databases is necessary. \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics. On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyze and discuss the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark. In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
the process of graph database benchmarking in the cloud focusing on a graph database application for social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space.
The workload generator of YCSB supports definition of new workload types. XGDBench involves basic operations read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using them 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties. A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.

@@

\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS. However, it is probably not maintained anymore.

>>>>

Currently there exists a number  of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks that have been designed specifically for graph databases is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed in a more general scope. Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary. \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics. On the basis of a review of applications of graph databases (namely social network analysis, proteomics or genetic interactions, recommendation systems, and travel planning and routing), the authors analyzed and discussed the characteristics of the graphs that appear in such applications and how they could influence benchmarking, different types of operations used in these applications and the characteristics of the evaluation setup of the benchmark. In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space.
The workload generator of YCSB supports definition of new workload types. XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties. A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.

@@

\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS. However, it is very likely that it is not maintained anymore due to the lack of updates provided.
